Article title

### 2019-07-16 NAR_DRAFT.tex
calibration and mutation rate table

@@

\begin{table}[b]
\tableparts{%
\caption{This is a table caption}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}lllll@{}}
\toprule
Col. head 1 & Col. head 2 & Col. head 3 & Col. head 4 & Col. head 5
\\
& (\%) & (s$^{-1}$) & (\%) & (s$^{-1}$)
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & --
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2
\\
\botrule
\end{tabular*}%
}
{This is a table footnote}
\end{table}

>>>>

\subsection{Calibration}
We use the Integrated Calibration Index to quantify the difference between MuTect and the Calibrated model \cite{Austin2019}.
Briefly, a loess-smoothed regression is fit by regressing the binary (T/F) variant classification against the reported posterior probability of a true variant for both MuTect and the Calibrated model (Figure \ref{NAR-fig1} \textbf{e}).
Plotting the smoothed regression predictions against the actual predictions would result in a diagonal line, and the Integrated Calibration Index is the total area between the result and a diagonal line.
\bkmcomment{Honestly, just putting the R code here exactly as Austin does is probably the best explanation?}

@@

\begin{table*}[b]
\tableparts{%
\caption{This is a table with auroc, auprc, ICI, and maybe fraction called?}
\label{table:01}%
}{%
\begin{tabular*}{\columnwidth}{@{}llllllll@{}}
\toprule
Experiment & $\mu$ & AUROC &  & AUPRC & & ICI & 
\\
& & MuTect & Calibrated & MuTect & Calibrated & MuTect & Calibrated
\\
\colrule
Row 1 & Row 1 & Row 1 & -- & -- &&&
\\
Row 2 & Row 2 & Row 2 & Row 2 & Row 2 &&&
\\
\botrule
\end{tabular*}%
}
{AUROC/AUPRC = area under ROC/PRC curve. ICI = Integrated calibration index}
\end{table*}
